---
title: "APPENDIX"
author: "Nathan Green"
date: "1 March 2016"
output: 
  word_document: 
    keep_md: yes
    toc: yes
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, comment = NA, results = "hide")
```


# QFN_TSPOT-HIV-noindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-HIV-noindeterminates-RUNS.Rmd'}
```

# indiv-dectree_QFN_TSPOT-HIV-WITHindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-HIV-WITHindeterminates-RUNS.Rmd'}
```

# indiv-dectree_QFN_TSPOT-HIVneg-noindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-HIVneg-noindeterminates-RUNS.Rmd'}
```

# indiv-dectree_QFN_TSPOT-HIVneg-WITHindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-HIVneg-WITHindeterminates-RUNS.Rmd'}
```

# indiv-dectree_QFN_TSPOT-HIVpos-noindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-HIVpos-noindeterminates-RUNS.Rmd'}
```

# indiv-dectree_QFN_TSPOT-HIVpos-WITHindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-HIVpos-WITHindeterminates-RUNS.Rmd'}
```

# indiv-dectree_QFN_TSPOT-noindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-noindeterminates-RUNS.Rmd'}
```

# indiv-dectree_QFN_TSPOT-WITHindeterminates

```{r child = 'SENSITIVITY_QFN_TSPOT-WITHindeterminates-RUNS.Rmd'}
```

<!---

##TODO##
## update

# 25quantiles-basecase-QFN-TSPOT

```{r child = '25quantiles-basecase-QFN-TSPOT.Rmd'}
```

# 65quantiles-basecase-QFN-TSPOT

```{r child = '65quantiles-basecase-QFN-TSPOT.Rmd'}
```

-->




